---
title: "RSA SCR PPV"
author: "Carlos Ventura-Bort"
date: "2023-09-04"
output: html_document
---

``` {r,include=FALSE}
#Adapt path accordingly
#load funcitons
source ('C:/Users/cvent/Desktop/RESEARCH/RSA_LondorfLab/RSAFunctions_only150923.R') 
#Variable to load data and avoid redoing all analysis. 
loadData<-1
if (loadData==1){
  load("RSA_SCR_Pic_VB22_Def.RData")
loadData<-1
}
#Set the wd
setwd("C:/Users/cvent/Desktop/RESEARCH/RSA_LondorfLab")
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


``` {r,include=FALSE}
#######
##Libraries
library(base)
library(psycho)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(fs)
library (lme4)
library(lmerTest)
library(sjPlot)
library(rstatix)
library(Hmisc)
# install.packages("extrafont")
library(extrafont)
library (ggbeeswarm)
library(BayesFactor)
library(bayestestR)
library(glue)
library(viridis)
library(ggpubr)
library(ggExtra)
#################################################
### Load Fonts for figures
#################################################
loadfonts(device="win")       #Register fonts for Windows bitmap output
windowsFonts(Times=windowsFont("Times"))
```

# Outline  
## *RSA from Ventura-Bort et al., 2022:*
## **Passive Picture Viewing Task**
### Skin Conductance Response: Vector or Amplitude?  
### Model Testing of Arousal: Nearest Neighborhood, Anna Karenina (AK) and inverted AK  
### Model Testing Beyond Arousal

##  **Vector or Amplitude?** 
### Are vector- and amplitude-based RSMs similar to each other?

```{r, readRDS myData2,include=FALSE }
#load the data
if (loadData==0){
  SCR_RSM<-readRDS("SCR_RSM.rds") 
#------------------------
#Select Task Pasive Picture viewing
PicEdaAro<-SCR_RSM  %>%
  filter(Task_def==1)
PicEdaAro$Category<-ifelse(PicEdaAro$trial_type==2,"Pl",
                           ifelse(PicEdaAro$trial_type==4,"Un","Ne"))
PicEdaAroMod<-PicEdaAro%>%
  select(Vp_ratings,Category, Aro, EDA_mean_log) 

#Matrix should contain VP, Behavioral Variable (e.g., Aro), 
# variable coding the sorting (sortAro), Variables for the vector (variables containing EDA)
PicEdaAro<-PicEdaAro%>%
  select(Vp_ratings,sortAro, contains("EDA"),- contains("EDA_mean")) 
#rename to favor the function. 
PicEdaAro<-PicEdaAro%>%
  rename(sort= sortAro)


#----------------------------------------------------------------
#Create Matrix based on single datapoints for EDA Amplitudes
PicEdaArosV<-SCR_RSM  %>%
  filter(Task_def==1)%>%
  dplyr::select(Vp_ratings, sortAro,EDA_mean_log)
PicEdaArosV<-PicEdaArosV%>%
  dplyr:: rename(sort= sortAro)

#----------------- DEFINE PARAMETERS FOR RUNING RSMVector for EDA and AROUSAL
# OriginalData<-PicEdaAro
nVariables<-36 # this variable defines the number of cells e.g., pictures presented
CharContainingNumberFromVector<-4 #Character containing number from variables coding vector.
#e.g., EDA1, EDA2, EDA3... the character is 4: 1, 2, 3...
### Select the variables needed for the loop: VP, Variable sorting, Vector values
VariableType<-"SCR_Vector"
sortType<- "Arousal"
OriginalData<-PicEdaAro

RSMVector(PicEdaAro,nVariables,CharContainingNumberFromVector,VariableType,sortType)

#----------------- DEFINE PARAMETERS FOR RUNING RSMSingle for Amplitudes for EDA and AROUSAL
# OriginalData<-PicEdaArosV
MaxValue<- max(PicEdaArosV$EDA_mean_log, na.rm=T)
nVariables<-36 # this variable defines the number of cells e.g., pictures presented
CharContainingNumberFromVector<-4 #Character containing number from variables coding vector.
#e.g., EDA1, EDA2, EDA3... the character is 4: 1, 2, 3...
### Select the variables needed for the loop: VP, Variable sorting, Vector values
VariableType<-"SCR_Single"
sortType<- "Arousal"

RSMSingleValue(PicEdaArosV,nVariables,CharContainingNumberFromVector,VariableType,sortType, MaxValue)

#Compare Vector and Amplitude Variable at a single level
Model<-"SCRVector"
Data<- "SCRSingle"
RSMIndividual(SCR_Vector_corr_prep_all,SCR_Single_corr_prep_all,Model,Data)

#---------------------
seedPer<-55
nPermutations<-10000
VariableOriginal<-"SCR_Single"
VariableModel<- "SCR_Vector"
# OriginalData<-SCR_Single_corr_prep_all
# ModelData<-Behav_Single_corr_prep_all
PermutationTest(SCR_Single_corr_prep_all,SCR_Vector_corr_prep_all,VariableOriginal,VariableModel,nPermutations,seedPer)
}

#----- Combined vector and single value
SCR_Single_corr_prep_allF<-SCR_Single_corr_prep_all%>%
select(var1, var2, mean_all)
SCR_Single_corr_prep_allF$Similarity<-SCR_Single_corr_prep_allF$mean_all

SCR_Vector_corr_prep_allF<- SCR_Vector_corr_prep_all%>% select(var1, var2, mean_all)
SCR_Vector_corr_prep_allF$Similarity<-SCR_Vector_corr_prep_allF$mean_all


SCR_Vector_corr_prep_allFDown<-SCR_Vector_corr_prep_allF%>% filter(var1<var2)

SCR_Single_corr_prep_allFUp<- SCR_Single_corr_prep_allF%>% filter(var1>var2)
SingleVectorSCR<- rbind(SCR_Single_corr_prep_allFUp,SCR_Vector_corr_prep_allFDown)
library(ggnewscale)

dataOriginal<-SingleVectorSCR#data coming up from RSM functions it should contain the variable mean_all
mypalette<- numeric()#colors
minimum<-numeric()#scale
maximum<-numeric()# scale
Category<- "trials" # VP or trials
Participant<- "Similarity" # factor() #if individual participants are to be selected,
sortType<- "Arousal" #variable to sort on
PlotMatrixCombined(dataOriginal, minimum,maximum,Category,sortType,Participant, mypalette)


```

```{r}

     # ggarrange(SCR_Vector_Arousal_RSM,SCR_Single_Arousal_RSM ,
     #        # SCRVector_SCRSingle_IndividualPlot, SCR_Single_SCR_Vector_PermOutput[["Output"]][["PermutationPlot"]],
     #        labels = c("A", "B" ),
     #        ncol = 2, nrow =1, widths = c(10,10))

SCR_Single_Arousal_RSM
SCR_Vector_Arousal_RSM
SCRVector_SCRSingle_IndividualPlot
SCR_Single_SCR_Vector_PermOutput[["Output"]][["PermutationPlot"]]
SCR_Single_SCR_Vector_PermOutput[["Output"]][["Summary"]]
         
```

## *Models of Arousal*  

### the RSMs of SCR will be tested against two models: 
the Nearest Neighborhood model which assumes that the closer trials are in arousal, the more similar they are  
from the Anna Karenina (AK) model which assumes that trials with high arousal will be more similar to each other than those rates as low arousal,
we will derive the inverted model (Inverted AK Model), which assumes that lower values of arousal are similar to each other, but higher values are more dissimilar
```{r, readRDS myData3,include=FALSE }
#Create Matrix based on single BEHAVIORAL
if (loadData==0){
PicBehaArosV<-SCR_RSM  %>%
  filter(Task_def==1)%>%
  dplyr::select(Vp_ratings, sortAro,Aro)
PicBehaArosV<-PicBehaArosV%>%
  rename(Behavioral= Aro)%>%
  rename(sort= sortAro)
# OriginalData<-PicBehaArosV
MaxValue<- max(PicBehaArosV$Behavioral, na.rm=T)

nVariables<-36 # this variable defines the number of cells e.g., pictures presented
CharContainingNumberFromVector<-3 #Character containing number from variables coding vector.
#e.g., EDA1, EDA2, EDA3... the character is 4: 1, 2, 3...
### Select the variables needed for the loop: VP, Variable sorting, Vector values
VariableType<-"Behav_Single_NN"
sortType<- "Arousal"

RSMSingleValue(PicBehaArosV,nVariables,CharContainingNumberFromVector,VariableType,sortType, MaxValue)

VariableType<-"Behav_Single_AK"
sortType<- "Arousal"

RSMSingleValueAK(PicBehaArosV,nVariables,CharContainingNumberFromVector,VariableType,sortType, MaxValue)

VariableType<-"Behav_Single_invAK"
sortType<- "Arousal"

RSMSingleValueinvAK(PicBehaArosV,nVariables,CharContainingNumberFromVector,VariableType,sortType, MaxValue)

}
```

```{r}
Behav_Single_NN_Arousal_RSM
Behav_Single_AK_Arousal_RSM
Behav_Single_invAK_Arousal_RSM


```

### Vector-and amplitude-based model tested againt NN Model 
```{r, readRDS myData41,include=FALSE }
if (loadData==0){

#------------ VECtOR------------------
Model<-"AroRatings_NN"
Data<- "SCR_Vector"
RSMIndividual(SCR_Vector_corr_prep_all,Behav_Single_NN_corr_prep_all,Model,Data)

#  Permutation test SCR Vector and Arousal Ratings NN
seedPer<-55
nPermutations<-10000
VariableOriginal<-"SCR_Vector"
VariableModel<- "AroRatings_NN"

PermutationTest(SCR_Vector_corr_prep_all,Behav_Single_NN_corr_prep_all,VariableOriginal,VariableModel,nPermutations,seedPer)


#------------ Amplitude------------------
Model<-"AroRatings_NN"
Data<- "SCR_Single"
RSMIndividual(SCR_Single_corr_prep_all,Behav_Single_NN_corr_prep_all,Model,Data)

#  Permutation test SCR Single and Arousal Ratings NN
seedPer<-55
nPermutations<-10000
VariableOriginal<-"SCR_Single"
VariableModel<- "AroRatings_NN"

PermutationTest(SCR_Single_corr_prep_all,Behav_Single_NN_corr_prep_all,VariableOriginal,VariableModel,nPermutations,seedPer)
}
```


```{r}
ggarrange(AroRatings_NN_SCR_Vector_IndividualPlot,AroRatings_NN_SCR_Single_IndividualPlot ,
            labels = c("Vector", "Single" ),
          hjust=-5,
            ncol = 2, nrow =1, widths = c(5,5))

 ggarrange( SCR_Vector_AroRatings_NN_PermOutput[["Output"]][["PermutationPlot"]],
            SCR_Single_AroRatings_NN_PermOutput[["Output"]][["PermutationPlot"]],
            labels = c("Vector", "Single" ),
                  hjust=-2,
            ncol = 1, nrow =2, widths = c(10,10))
```

### Vector-and amplitude-based model tested againt invAK Model 
```{r, readRDS myData44,include=FALSE }
if (loadData==0){

#------------ VECtOR------------------
Model<-"AroRatings_invAK"
Data<- "SCR_Vector"
RSMIndividual(SCR_Vector_corr_prep_all,Behav_Single_invAK_corr_prep_all,Model,Data)

#  Permutation test SCR Vector and Arousal Ratings NN
seedPer<-55
nPermutations<-10000
VariableOriginal<-"SCR_Vector"
VariableModel<- "AroRatings_invAK"

PermutationTest(SCR_Vector_corr_prep_all,Behav_Single_invAK_corr_prep_all,VariableOriginal,VariableModel,nPermutations,seedPer)


#------------ Amplitude------------------
Model<-"AroRatings_invAK"
Data<- "SCR_Single"
RSMIndividual(SCR_Single_corr_prep_all,Behav_Single_invAK_corr_prep_all,Model,Data)

#  Permutation test SCR Single and Arousal Ratings NN
seedPer<-55
nPermutations<-10000
VariableOriginal<-"SCR_Single"
VariableModel<- "AroRatings_invAK"

PermutationTest(SCR_Single_corr_prep_all,Behav_Single_invAK_corr_prep_all,VariableOriginal,VariableModel,nPermutations,seedPer)



t.test(AroRatings_NN_SCR_Single_tableCorrelation$Correlation, mu = 0)
t.test(AroRatings_invAK_SCR_Single_tableCorrelation$Correlation, mu = 0)
#---------- BAYES t-test: 
 extractBF(ttestBF( AroRatings_invAK_SCR_Single_tableCorrelation$Correlation), onlybf = TRUE)
   extractBF(ttestBF( AroRatings_NN_SCR_Single_tableCorrelation$Correlation), onlybf = TRUE)



#Combine two histograms in one
p1<-matrix(unlist(SCR_Single_AroRatings_invAK_PermOutput[["PermutationTest"]][["value"]]), ncol=1)
p2<-matrix(unlist(SCR_Single_AroRatings_NN_PermOutput[["PermutationTest"]][["value"]]), ncol=1)
p1<-tibble(p1)

p2<-tibble(p2)
p1$model<-"inverted AK"
p2$model<-"NN"
names(p1)<-c("permutation","model")
  names(p2)<- c("permutation","model")

ptotal<-rbind(p1,p2)

similarity1<-matrix(unlist(SCR_Single_AroRatings_invAK_PermOutput[["Similarity"]]),ncol=1)
similarity2<-matrix(unlist(SCR_Single_AroRatings_NN_PermOutput[["Similarity"]]),ncol=1)
similarity1$model<-"inverted AK"
similarity2$model<-"NN"
names(similarity1)<-c("Similarity","model")
  names(similarity2)<- c("Similarity","model")
similaritytotal<-as.data.frame(rbind(similarity1,similarity2))
similaritytotal$Similarity<-as.numeric(similaritytotal$Similarity)
similaritytotal$model<-as.factor(similaritytotal$model)


th1<-matrix(unlist(SCR_Single_AroRatings_invAK_PermOutput[["PermutationTest"]][["value"]][9500]), ncol=1)
th2<-matrix(unlist(SCR_Single_AroRatings_NN_PermOutput[["PermutationTest"]][["value"]][9500]), ncol=1)
th1<-tibble(th1)

th2<-tibble(th2)
th1$model<-"inverted AK"
th2$model<-"NN"
names(th1)<-c("threshold","model")
  names(th2)<- c("threshold","model")

thtotal<-rbind(th1,th2)


test<-
  ggplot(ptotal, aes(permutation, fill = model)) + geom_density(alpha = 0.2)+     scale_fill_manual(values=c('darkgoldenrod1','darkmagenta'))+
      scale_y_continuous(expand = expansion(mult = c(0, .1)))

test+geom_vline(data=similaritytotal, aes(xintercept=Similarity),
            color= c('darkgoldenrod1','darkmagenta'), linetype="solid",size = 2)+
    geom_vline(data=thtotal, aes(xintercept=threshold),
            color= c('darkgoldenrod1','darkmagenta'), linetype="dashed",size = 2)+
  theme_classic()+
      theme(axis.text.x= element_text(size=15),
             axis.text.y= element_text(size=15),
             axis.title.x = element_text( size=15,face="bold"),
             axis.title.y = element_text( size=15,face="bold"))


#RSMs combined
SCR<-SCR_Single_corr_prep_all%>% select(var1, var2, mean_all)
SCR$Similarity<-SCR$mean_all
invAK<- Behav_Single_invAK_corr_prep_all%>% select(var1, var2, mean_all)
invAK$Similarity<-invAK$mean_all
NN<- Behav_Single_NN_corr_prep_all%>% select(var1, var2, mean_all)
NN$Similarity<-NN$mean_all
SCRDown<-SCR%>% filter(var1<var2)
invAKUp<- invAK%>% filter(var1>var2)
NNUp<- NN%>%filter(var1>var2)

invAKSCR<- rbind(SCRDown,invAKUp)
NNSCR<- rbind(SCRDown, NNUp)
library(ggnewscale)

dataOriginal<-invAKSCR#data coming up from RSM functions it should contain the variable mean_all
mypalette<- numeric()#colors
minimum<-numeric()#scale
maximum<-numeric()# scale
Category<- "trials" # VP or trials
Participant<- "Similarity" # factor() #if individual participants are to be selected,
sortType<- "Arousal" #variable to sort on
PlotMatrixCombined(dataOriginal, minimum,maximum,Category,sortType,Participant, mypalette)



dataOriginal<-NNSCR#data coming up from RSM functions it should contain the variable mean_all
mypalette<- numeric()#colors
minimum<-numeric()#scale
maximum<-numeric()# scale
Category<- "trials" # VP or trials
Participant<- "Similarity" # factor() #if individual participants are to be selected,
sortType<- "Arousal" #variable to sort on
PlotMatrixCombined(dataOriginal, minimum,maximum,Category,sortType,Participant, mypalette)

#Plot individual Data
library(ggridges) # ridgeline plot
library(tidyr) # long format
library(colorBlindness)
library(RColorBrewer)
test = cbind(AroRatings_invAK_SCR_Single_tableCorrelation,
             AroRatings_NN_SCR_Single_tableCorrelation)
test2 = test[c(1,2,4)]
names(test2)<-c("VP", "inverted AK", "NN")
long_data2 <- gather(test2, key = "model", value = "Similarity", 2:3)

ggplot(long_data2, aes(x=Similarity, y=model, fill = model))  + geom_density_ridges()+
    scale_fill_brewer(palette = 4) +
  theme_ridges() + theme(legend.position = "none")+
  labs(x = "rho value", y = "Regressor")+
  geom_vline(xintercept = 0, color = "red", linetype = "dashed")
# colorblind friendly
cols = c( 'darkgoldenrod1','darkmagenta')

# "#004949"  ,   "#009292" ,    "#FF6DB6"    , "#FFB6DB" ,    "#490092"  ,   "#006DDB" ,
#     "#B66DFF"  ,   "#6DB6FF"   ,  "#B6DBFF")
ggplot(long_data2, aes(x=Similarity, y=model, fill = model, alpha = .2))  + 
  theme_classic() + theme(legend.position = "none")+
  labs(x = "Similarity", y = "")+
  scale_y_discrete(expand = expansion(add = c(0,1)))+
  geom_density_ridges(quantile_lines=TRUE,bandwidth = 0.1,
                      quantile_fun=function(x,...)mean(x), size = 1) +
  scale_fill_manual(values = cols, )+
  geom_vline(xintercept = 0, color = "black", linetype = "dashed", size = 1)+
  scale_x_continuous(breaks= c(-.5,-.25,0, .25,.5,.75), limits= c(-.5,.8))+
  theme(axis.text.x= element_text(size=20),
        axis.text.y= element_blank(), #element_text(size=15),
        axis.title.x =  element_text( size=25,face="bold"),
        axis.title.y = element_text( size=15,face="bold"))



}
```

```{r}
ggarrange(AroRatings_invAK_SCR_Vector_IndividualPlot,AroRatings_invAK_SCR_Single_IndividualPlot ,
            labels = c("Vector", "Single" ),   hjust=-5,
            ncol = 2, nrow =1, widths = c(10,10))

 ggarrange( SCR_Vector_AroRatings_invAK_PermOutput[["Output"]][["PermutationPlot"]],
            SCR_Single_AroRatings_invAK_PermOutput[["Output"]][["PermutationPlot"]],
            labels = c("Vector", "Single" ),   hjust=-2,
            ncol = 1, nrow =2, widths = c(10,10))
```

### Test the unique contribution of each model (i.e., NN and invAK)  for Vector-and amplitude-based 
#### **VECTOR**
```{r, readRDS myData4,include=FALSE }
#------------ VECtOR------------------
if (loadData==0){

#PermutationwithRegression
OriginalData<- SCR_Vector_corr_prep_all
ModelData1<-Behav_Single_invAK_corr_prep_all
ModelData2<- Behav_Single_NN_corr_prep_all
VariableOriginal<-"SCR_Vector"
VariableModel1<- "AroRatings_invAK"
VariableModel2<- "AroRatings_NN"
seedPer<-49
nPermutations<-10000
PlotRSMReg<-1
Category = "Trials"

PermutationTestRegModels(OriginalData,ModelData1,
                         ModelData2,VariableOriginal,VariableModel1,VariableModel2,Category,
                         nPermutations,seedPer,PlotRSMReg)


#Individual Data
RSMIndividualRegression(OriginalData,ModelData1,ModelData2,VariableOriginal,VariableModel1,VariableModel2) 


t.test(SCRSingle_AroRatings_invAK_AroRatings_NN_tableRegression$Similarity_SCR_Single_AroRatings_invAK, mu = 0)
t.test(SCRSingle_AroRatings_invAK_AroRatings_NN_tableRegression$Similarity_SCR_Single_AroRatings_NN, mu = 0)
#---------- BAYES t-test: 
 extractBF(ttestBF( SCRSingle_AroRatings_invAK_AroRatings_NN_tableRegression$Similarity_SCR_Single_AroRatings_invAK), onlybf = TRUE)
   extractBF(ttestBF( SCRSingle_AroRatings_invAK_AroRatings_NN_tableRegression$Similarity_SCR_Single_AroRatings_NN), onlybf = TRUE)



#Combine two histograms in one
p1<-matrix(unlist(SCR_Single_AroRatings_invAK_AroRatings_NN_PermOutputRegr[["Model1"]][["PermutationTest"]][["value"]]), ncol=1)
p2<-matrix(unlist(SCR_Single_AroRatings_invAK_AroRatings_NN_PermOutputRegr[["Model2"]][["PermutationTest"]][["value"]]), ncol=1)
p1<-tibble(p1)

p2<-tibble(p2)
p1$model<-"inverted AK"
p2$model<-"NN"
names(p1)<-c("permutation","model")
  names(p2)<- c("permutation","model")

ptotal<-rbind(p1,p2)

similarity1<-matrix(unlist(SCR_Single_AroRatings_invAK_AroRatings_NN_PermOutputRegr[["Model1"]][["Similarity"]]),ncol=1)
similarity2<-matrix(unlist(SCR_Single_AroRatings_invAK_AroRatings_NN_PermOutputRegr[["Model2"]][["Similarity"]]),ncol=1)
similarity1$model<-"inverted AK"
similarity2$model<-"NN"
names(similarity1)<-c("Similarity","model")
  names(similarity2)<- c("Similarity","model")
similaritytotal<-as.data.frame(rbind(similarity1,similarity2))
similaritytotal$Similarity<-as.numeric(similaritytotal$Similarity)
similaritytotal$model<-as.factor(similaritytotal$model)


th1<-matrix(unlist(SCR_Single_AroRatings_invAK_AroRatings_NN_PermOutputRegr[["Model1"]][["PermutationTest"]][["value"]][9500]), ncol=1)
th2<-matrix(unlist(SCR_Single_AroRatings_invAK_AroRatings_NN_PermOutputRegr[["Model2"]][["PermutationTest"]][["value"]][9500]), ncol=1)
th1<-tibble(th1)

th2<-tibble(th2)
th1$model<-"inverted AK"
th2$model<-"NN"
names(th1)<-c("threshold","model")
  names(th2)<- c("threshold","model")

thtotal<-rbind(th1,th2)


test<-
  ggplot(ptotal, aes(permutation, fill = model)) + geom_density(alpha = 0.2)+     scale_fill_manual(values=c('darkgoldenrod1','darkmagenta'))+
      scale_y_continuous(expand = expansion(mult = c(0, .1)))

test+geom_vline(data=similaritytotal, aes(xintercept=Similarity),
            color= c('darkgoldenrod1','darkmagenta'), linetype="solid",size = 2)+
    geom_vline(data=thtotal, aes(xintercept=threshold),
            color= c('darkgoldenrod1','darkmagenta'), linetype="dashed",size = 2)+
  theme_classic()+
      theme(axis.text.x= element_text(size=15),
             axis.text.y= element_text(size=15),
             axis.title.x = element_text( size=15,face="bold"),
             axis.title.y = element_text( size=15,face="bold"))


#RSMs combined
SCR<-SCR_Single_corr_prep_all%>% select(var1, var2, mean_all)
SCR$Similarity<-SCR$mean_all
invAK<- SCR_Single_AroRatings_invAK_AroRatings_NN_PermOutputRegr[["Ouput"]][["RSMPlotRegressionM1"]][["data"]]%>% select(var1, var2, mean_all)
invAK$Similarity<-invAK$mean_all
NN<- SCR_Single_AroRatings_invAK_AroRatings_NN_PermOutputRegr[["Ouput"]][["RSMPlotRegressionM2"]][["data"]]%>% select(var1, var2, mean_all)
NN$Similarity<-NN$mean_all
SCRDown<-SCR%>% filter(var1<var2)
invAKUp<- invAK%>% filter(var1>var2)
NNUp<- NN%>%filter(var1>var2)

invAKSCR<- rbind(SCRDown,invAKUp)
NNSCR<- rbind(SCRDown, NNUp)
library(ggnewscale)

dataOriginal<-invAKSCR#data coming up from RSM functions it should contain the variable mean_all
mypalette<- numeric()#colors
minimum<-numeric()#scale
maximum<-numeric()# scale
Category<- "trials" # VP or trials
Participant<- "Similarity" # factor() #if individual participants are to be selected,
sortType<- "Arousal" #variable to sort on
PlotMatrixCombined(dataOriginal, minimum,maximum,Category,sortType,Participant, mypalette)



dataOriginal<-NNSCR#data coming up from RSM functions it should contain the variable mean_all
mypalette<- numeric()#colors
minimum<-numeric()#scale
maximum<-numeric()# scale
Category<- "trials" # VP or trials
Participant<- "Similarity" # factor() #if individual participants are to be selected,
sortType<- "Arousal" #variable to sort on
PlotMatrixCombined(dataOriginal, minimum,maximum,Category,sortType,Participant, mypalette)



#Plot individual Data
library(ggridges) # ridgeline plot
library(tidyr) # long format
library(colorBlindness)
library(RColorBrewer)

test2 = SCRSingle_AroRatings_invAK_AroRatings_NN_tableRegression
names(test2)<-c("VP", "inverted AK", "NN")
long_data2 <- gather(test2, key = "model", value = "Similarity", 2:3)
# colorblind friendly
cols = c( 'darkgoldenrod1','darkmagenta')

# "#004949"  ,   "#009292" ,    "#FF6DB6"    , "#FFB6DB" ,    "#490092"  ,   "#006DDB" ,
#     "#B66DFF"  ,   "#6DB6FF"   ,  "#B6DBFF")
ggplot(long_data2, aes(x=Similarity, y=model, fill = model, alpha = .2))  + 
  theme_classic() + theme(legend.position = "none")+
  labs(x = "Similarity", y = "")+
  scale_y_discrete(expand = expansion(add = c(0,1)))+
  geom_density_ridges(quantile_lines=TRUE,bandwidth = 0.1,
                      quantile_fun=function(x,...)mean(x), size = 1) +
  scale_fill_manual(values = cols, )+
  geom_vline(xintercept = 0, color = "black", linetype = "dashed", size = 1)+
  scale_x_continuous(breaks= c(-.5,-.25,0, .25,.5,.75), limits= c(-.5,.8))+
  theme(axis.text.x= element_text(size=20),
        axis.text.y= element_blank(), #element_text(size=15),
        axis.title.x =  element_text( size=25,face="bold"),
        axis.title.y = element_text( size=15,face="bold"))

}
```

```{r}
 ggarrange(SCR_Vector_AroRatings_invAK_AroRatings_NN_IndividualPlotRegression[[1]],
SCR_Vector_AroRatings_invAK_AroRatings_NN_IndividualPlotRegression[[2]],
            labels = c("", "" ),   vjust=-7,
            ncol = 2, nrow =1, widths = c(5,5))


 ggarrange(SCR_Vector_AroRatings_invAK_AroRatings_NN_PermOutputRegr[["Ouput"]][["RSMPlotRegressionM1"]],
SCR_Vector_AroRatings_invAK_AroRatings_NN_PermOutputRegr[["Ouput"]][["RSMPlotRegressionM2"]],
            labels = c("", "" ),   vjust=-7,
            ncol = 2, nrow =1, widths = c(5,5))

ggarrange( SCR_Vector_AroRatings_invAK_AroRatings_NN_PermOutputRegr[["Ouput"]][["PermutationPlotM1"]],
SCR_Vector_AroRatings_invAK_AroRatings_NN_PermOutputRegr[["Ouput"]][["PermutationPlotM2"]],
            labels = c("iAK", "NN"),   vjust=(12),
            ncol = 1, nrow =2, widths = c(5,5))
```

  
#### **Amplitude**  
```{r, readRDS myData5,include=FALSE }
#------------ VECtOR------------------
if (loadData==0){

#PermutationwithRegression
OriginalData<- SCR_Single_corr_prep_all
ModelData1<-Behav_Single_invAK_corr_prep_all
ModelData2<- Behav_Single_NN_corr_prep_all
VariableOriginal<-"SCR_Single"
VariableModel1<- "AroRatings_invAK"
VariableModel2<- "AroRatings_NN"
seedPer<-49
nPermutations<-10000
PlotRSMReg<-1
Category = "Trials"

PermutationTestRegModels(OriginalData,ModelData1,
                         ModelData2,VariableOriginal,VariableModel1,VariableModel2,Category,
                         nPermutations,seedPer,PlotRSMReg)

RSMIndividualRegression(OriginalData,ModelData1,ModelData2,VariableOriginal,VariableModel1,VariableModel2) 

}

```

```{r}
ggarrange(SCR_Single_AroRatings_invAK_AroRatings_NN_IndividualPlotRegression[[1]],
SCR_Single_AroRatings_invAK_AroRatings_NN_IndividualPlotRegression[[2]],
            labels = c("", "" ),   vjust=-7,
            ncol = 2, nrow =1, widths = c(5,5))


 ggarrange( SCR_Single_AroRatings_invAK_AroRatings_NN_PermOutputRegr[["Ouput"]][["RSMPlotRegressionM1"]],
SCR_Single_AroRatings_invAK_AroRatings_NN_PermOutputRegr[["Ouput"]][["RSMPlotRegressionM2"]],
            labels = c("", "" ),   vjust=-7,
            ncol = 2, nrow =1, widths = c(5,5))

ggarrange( SCR_Single_AroRatings_invAK_AroRatings_NN_PermOutputRegr[["Ouput"]][["PermutationPlotM1"]],
SCR_Single_AroRatings_invAK_AroRatings_NN_PermOutputRegr[["Ouput"]][["PermutationPlotM2"]],
            labels = c("iAK", "NN"),   vjust=(12),
            ncol = 1, nrow =2, widths = c(5,5))
```

  
### Relationship between Similarity measures of the NN and invAK Model  
```{r, readRDS myData6,include=FALSE }
if (loadData==0){
#VECTOR
VecSimComparison<-inner_join(AroRatings_invAK_SCR_Vector_tableCorrelation,AroRatings_NN_SCR_Vector_tableCorrelation,
                             by = "VP", suffix = c("invAK","NN"))

cor.testVecSimCom<-cor.test(VecSimComparison$CorrelationinvAK,VecSimComparison$CorrelationNN)

 p<- ggplot(VecSimComparison, aes(x=CorrelationinvAK, y=CorrelationNN)) +
  geom_point(shape=21, color = "black",fill="gray75", size=5)+
   theme(legend.position="none")+
   stat_smooth(method = "lm",
              formula = y ~ x,
              geom = "smooth", color = "red")+
   theme_classic()+
 stat_cor(method = "pearson")+
       ggtitle("SCR Vector")
   
SCRVectorCorrModComp<- ggMarginal(p ,type="histogram", fill = "slateblue", xparams = list(  bins=100))
   
#Amplitude
SingleSimComparison<-inner_join(AroRatings_invAK_SCR_Single_tableCorrelation,AroRatings_NN_SCR_Single_tableCorrelation,
                             by = "VP", suffix = c("invAK","NN"))

cor.testSingSimCom<-cor.test(SingleSimComparison$CorrelationinvAK,SingleSimComparison$CorrelationNN)

 p<- ggplot(SingleSimComparison, aes(x=CorrelationinvAK, y=CorrelationNN)) +
  geom_point(shape=21, color = "black",fill="gray75", size=5)+
   theme(legend.position="none")+
   stat_smooth(method = "lm",
              formula = y ~ x,
              geom = "smooth", color = "red")+
   theme_classic()+
 stat_cor(method = "pearson")+
       ggtitle("SCR Single")
   
SCRSingleCorrModComp<- ggMarginal(p ,type="histogram", fill = "slateblue", xparams = list(  bins=100))
} 
```

```{r}
ggarrange( SCRVectorCorrModComp,SCRSingleCorrModComp,
            labels = c("", ""),   vjust=(12),
            ncol = 1, nrow =2, widths = c(5))
```
### Plot individual participants as example:   
#### High in invAK and and in NN Model
``` {r}
#Plot VP 
#-------------- Plot RSM Matrix
dataOriginal<-SCR_Single_corr_prep_all#data coming up from RSM functions it should contain the variable mean_all
mypalette<- numeric()#colors
minimum<-numeric()#scale
maximum<-numeric()# scale
Category<- "trials" # VP or trials
Participant<- "VP19" # factor() #if individual participants are to be selected,
sortType<- "Arousal" #variable to sort on
PlotMatrix(dataOriginal, minimum,maximum,Category,sortType,Participant, mypalette)

```


#### High in invAK and close to 0 in NN Model  
``` {r}
#Plot VP 
#-------------- Plot RSM Matrix
dataOriginal<-SCR_Single_corr_prep_all#data coming up from RSM functions it should contain the variable mean_all
mypalette<- numeric()#colors
minimum<-numeric()#scale
maximum<-numeric()# scale
Category<- "trials" # VP or trials
Participant<- "VP46" # factor() #if individual participants are to be selected,
sortType<- "Arousal" #variable to sort on
PlotMatrix(dataOriginal, minimum,maximum,Category,sortType,Participant, mypalette)
```


#### Low in invAK and moderate in NN Model
``` {r}
#Plot VP 
#-------------- Plot RSM Matrix
dataOriginal<-SCR_Single_corr_prep_all#data coming up from RSM functions it should contain the variable mean_all
mypalette<- numeric()#colors
minimum<-numeric()#scale
maximum<-numeric()# scale
Category<- "trials" # VP or trials
Participant<- "VP22" # factor() #if individual participants are to be selected,
sortType<- "Arousal" #variable to sort on
PlotMatrix(dataOriginal, minimum,maximum,Category,sortType,Participant, mypalette)

```

##  **Model Testing Beyond Arousal. Is the invAK the best fitting model? (analyses only performed for Amplitude-based RSM)**  
### Model Time  
```{r, readRDS myData7,include=FALSE }
if (loadData==0){
  #----------- MODEL TIME-----------------------
#Create Matrix based on single BEHAVIORAL
PicBehavArosVTime<-SCR_RSM  %>%
  filter(Task_def==1)%>%
  dplyr::select(Vp_ratings, sortAro,trial_order)
PicBehavArosVTime<-PicBehavArosVTime%>%
  rename(Behavioral= trial_order)%>%
  rename(sort= sortAro)
# OriginalData<-PicEdaArosV
MaxValue<- max(PicBehavArosVTime$Behavioral, na.rm=T)

nVariables<-36 # this variable defines the number of cells e.g., pictures presented
CharContainingNumberFromVector<-3 #Character containing number from variables coding vector.
#e.g., EDA1, EDA2, EDA3... the character is 4: 1, 2, 3...
### Select the variables needed for the loop: VP, Variable sorting, Vector values
VariableType<-"Behav_SingleTimeSortedbyArousal"
sortType<- "TimeSortedbyArousal"

RSMSingleValue(PicBehavArosVTime,nVariables,CharContainingNumberFromVector,VariableType,sortType, MaxValue)

Model<-"SCRSingle"
Data<- "TimeSortedByArousal"
RSMIndividual(SCR_Single_corr_prep_all,Behav_SingleTimeSortedbyArousal_corr_prep_all,Model,Data)


}
```


```{r}
SCRSingle_TimeSortedByArousal_IndividualPlot
```

### Test whether the invAK model is contributing beyond time  
```{r, readRDS myData8,include=FALSE }
if (loadData==0){
# Individual Regression
OriginalData<- SCR_Single_corr_prep_all
ModelData1<-Behav_Single_invAK_corr_prep_all
ModelData2<- Behav_SingleTimeSortedbyArousal_corr_prep_all
VariableOriginal<-"SCR_Single"
VariableModel1<- "AroRatings_invAK"
VariableModel2<- "Time_NN"

RSMIndividualRegression(OriginalData,ModelData1,ModelData2,VariableOriginal,VariableModel1,VariableModel2) 

#Amplitude
SingleSimComparisonTime<-inner_join(AroRatings_invAK_SCR_Single_tableCorrelation,SCRSingle_TimeSortedByArousal_tableCorrelation,
                             by = "VP", suffix = c("invAK","Time"))

cor.testSingSimComTime<-cor.test(SingleSimComparisonTime$CorrelationinvAK,SingleSimComparisonTime$CorrelationTime)

 p<- ggplot(SingleSimComparisonTime, aes(x=CorrelationinvAK, y=CorrelationTime)) +
  geom_point(shape=21, color = "black",fill="gray75", size=5)+
   theme(legend.position="none")+
   stat_smooth(method = "lm",
              formula = y ~ x,
              geom = "smooth", color = "red")+
   theme_classic()+
 stat_cor(method = "pearson")+
       ggtitle("SCR Single")
   
SCRSingleCorrModCompTime<- ggMarginal(p ,type="histogram", fill = "slateblue", xparams = list(  bins=100))
}
# save.image("RSA_SCR_Pic_VB22_Def.RData")

```

```{r}
SCRSingleCorrModCompTime

ggarrange(SCR_Single_AroRatings_invAK_Time_NN_IndividualPlotRegression[[1]],
SCR_Single_AroRatings_invAK_Time_NN_IndividualPlotRegression[[2]],
            labels = c("", "" ),   vjust=-7,
            ncol = 2, nrow =1, widths = c(5,5))



```


### Model Category (Pleasant, Unpleasant, Neutral)  
```{r, readRDS myData88,include=FALSE }
if (loadData==0){
 #----------------------------- MODEL Category --------------------------------------
PicBehavArosVCat<-SCR_RSM  %>%
  filter(Task_def==1)
  PicBehavArosVCat$Category<-ifelse(PicBehavArosVCat$trial_type==2,"Pl",
                           ifelse(PicBehavArosVCat$trial_type==4,"Un","Ne"))
    PicBehavArosVCat<-PicBehavArosVCat%>%
    dplyr::select(Vp_ratings, sortAro,length(PicBehavArosVCat))


PicBehavArosVCat<-PicBehavArosVCat%>%
  rename(Behavioral= Category)%>%
  rename(sort= sortAro)
# OriginalData<-PicEdaArosV
MaxValue<- 1
nVariables<-36 # this variable defines the number of cells e.g., pictures presented
CharContainingNumberFromVector<-3 #Character containing number from variables coding vector.
#e.g., EDA1, EDA2, EDA3... the character is 4: 1, 2, 3...
### Select the variables needed for the loop: VP, Variable sorting, Vector values
VariableType<-"Behav_SingleCategorySortedbyArousal"
sortType<- "CategorySortedbyArousal"

RSMSingleValueFactor(PicBehavArosVCat,nVariables,CharContainingNumberFromVector,VariableType,sortType, MaxValue)


Model<-"SCRSingle"
Data<- "Categorysortedbyarousal"
RSMIndividual(SCR_Single_corr_prep_all,Behav_SingleCategorySortedbyArousal_corr_prep_all,Model,Data)
 
 }
# save.image("RSA_SCR_Pic_VB22_Def.RData")

```

```{r}
SCRSingle_Categorysortedbyarousal_IndividualPlot
```


### Test whether the invAK model is contributing beyond Category
```{r, readRDS myData10,include=FALSE }
if (loadData==0){
# Individual Regression
OriginalData<- SCR_Single_corr_prep_all
ModelData1<-Behav_Single_invAK_corr_prep_all
ModelData2<- Behav_SingleCategorySortedbyArousal_corr_prep_all
VariableOriginal<-"SCR_Single"
VariableModel1<- "AroRatings_invAK"
VariableModel2<- "Category_Factor"

RSMIndividualRegression(OriginalData,ModelData1,ModelData2,VariableOriginal,VariableModel1,VariableModel2) 

#Amplitude
SingleSimComparisonCat<-inner_join(AroRatings_invAK_SCR_Single_tableCorrelation,SCRSingle_Categorysortedbyarousal_tableCorrelation,
                             by = "VP", suffix = c("invAK","Cat"))

cor.testSingSimComCat<-cor.test(SingleSimComparisonCat$CorrelationinvAK,SingleSimComparisonCat$CorrelationCat)

 p<- ggplot(SingleSimComparisonCat, aes(x=CorrelationinvAK, y=CorrelationCat)) +
  geom_point(shape=21, color = "black",fill="gray75", size=5)+
   theme(legend.position="none")+
   stat_smooth(method = "lm",
              formula = y ~ x,
              geom = "smooth", color = "red")+
   theme_classic()+
 stat_cor(method = "pearson")+
       ggtitle("SCR Single")
   
SCRSingleCorrModCompCat<- ggMarginal(p ,type="histogram", fill = "slateblue", xparams = list(  bins=100))
}
# save.image("RSA_SCR_Pic_VB22_Def.RData")

```

```{r}
SCRSingleCorrModCompCat

ggarrange(SCR_Single_AroRatings_invAK_Category_Factor_IndividualPlotRegression[[1]],
SCR_Single_AroRatings_invAK_Category_Factor_IndividualPlotRegression[[2]],
            labels = c("", "" ),   vjust=-7,
            ncol = 2, nrow =1, widths = c(5,5))



```



### Model Valence
```{r, readRDS myData9,include=FALSE }
if (loadData==0){
 #----------------------------- MODEL Valence --------------------------------------
PicBehavArosVVal<-SCR_RSM  %>%
  filter(Task_def==1)%>%
  dplyr::select(Vp_ratings, sortAro,Val)
PicBehavArosVVal<-PicBehavArosVVal%>%
  rename(Behavioral= Val)%>%
  rename(sort= sortAro)
# OriginalData<-PicEdaArosV
MaxValue<- max(PicBehavArosVVal$Behavioral, na.rm=T)

nVariables<-36 # this variable defines the number of cells e.g., pictures presented
CharContainingNumberFromVector<-3 #Character containing number from variables coding vector.
#e.g., EDA1, EDA2, EDA3... the character is 4: 1, 2, 3...
### Select the variables needed for the loop: VP, Variable sorting, Vector values
VariableType<-"Behav_SingleValSortedbyArousal"
sortType<- "ValSortedbyArousal"

RSMSingleValue(PicBehavArosVVal,nVariables,CharContainingNumberFromVector,VariableType,sortType, MaxValue)
 
Model<-"SCRSingle"
Data<- "ValSortedByArousal"
RSMIndividual(SCR_Single_corr_prep_all,Behav_SingleValSortedbyArousal_corr_prep_all,Model,Data)


}
# save.image("RSA_SCR_Pic_VB22_Def.RData")

```

```{r}
SCRSingle_ValSortedByArousal_IndividualPlot
```

### Test whether the invAK model is contributing beyond Valence
```{r, readRDS myData11,include=FALSE }
if (loadData==0){
# Individual Regression
OriginalData<- SCR_Single_corr_prep_all
ModelData1<-Behav_Single_invAK_corr_prep_all
ModelData2<- Behav_SingleValSortedbyArousal_corr_prep_all
VariableOriginal<-"SCR_Single"
VariableModel1<- "AroRatings_invAK"
VariableModel2<- "Valence_NN"

RSMIndividualRegression(OriginalData,ModelData1,ModelData2,VariableOriginal,VariableModel1,VariableModel2) 

#Amplitude
SingleSimComparisonVal<-inner_join(AroRatings_invAK_SCR_Single_tableCorrelation,SCRSingle_ValSortedByArousal_tableCorrelation,
                             by = "VP", suffix = c("invAK","Val"))

cor.testSingSimComVal<-cor.test(SingleSimComparisonVal$CorrelationinvAK,SingleSimComparisonVal$CorrelationVal)

 p<- ggplot(SingleSimComparisonVal, aes(x=CorrelationinvAK, y=CorrelationVal)) +
  geom_point(shape=21, color = "black",fill="gray75", size=5)+
   theme(legend.position="none")+
   stat_smooth(method = "lm",
              formula = y ~ x,
              geom = "smooth", color = "red")+
   theme_classic()+
 stat_cor(method = "pearson")+
       ggtitle("SCR Single")
   
SCRSingleCorrModCompVal<- ggMarginal(p ,type="histogram", fill = "slateblue", xparams = list(  bins=100))
}
# save.image("RSA_SCR_Pic_VB22_Def.RData")

```

```{r}
SCRSingleCorrModCompVal

ggarrange(SCR_Single_AroRatings_invAK_Valence_NN_IndividualPlotRegression[[1]],
SCR_Single_AroRatings_invAK_Valence_NN_IndividualPlotRegression[[2]],
            labels = c("", "" ),   vjust=-7,
            ncol = 2, nrow =1, widths = c(5,5))
```

### Model Category based on Arousal (Arousing, non-arousing images)
```{r, readRDS myData12,include=FALSE }
if (loadData==0){
 #----------------------------- MODEL Category 2 (arousing non-arousing) --------------------------------------
PicBehavArosVCat$Category2<-ifelse(PicBehavArosVCat$Behavioral=="Ne","No","Ye")
PicEdaArosVCat2<-PicBehavArosVCat  %>%
  dplyr::select(Vp_ratings, sort,Category2)
PicEdaArosVCat2<-PicEdaArosVCat2%>%
  rename(Behavioral= Category2)
# OriginalData<-PicEdaArosV
MaxValue<- 1
nVariables<-36 # this variable defines the number of cells e.g., pictures presented
CharContainingNumberFromVector<-3 #Character containing number from variables coding vector.
#e.g., EDA1, EDA2, EDA3... the character is 4: 1, 2, 3...
### Select the variables needed for the loop: VP, Variable sorting, Vector values
VariableType<-"Behav_SingleCategory2SortedbyArousal"
sortType<- "CategorySortedbyArousal"

RSMSingleValueFactor(PicEdaArosVCat2,nVariables,CharContainingNumberFromVector,VariableType,sortType, MaxValue)

Model<-"SCRSingle"
Data<- "Category2SortedbyArousal"
RSMIndividual(SCR_Single_corr_prep_all,Behav_SingleCategory2SortedbyArousal_corr_prep_all,Model,Data)

}
# save.image("RSA_SCR_Pic_VB22_Def.RData")

```


```{r}
SCRSingle_Category2SortedbyArousal_IndividualPlot
```
### Test whether the invAK model is contributing beyond Category 2
```{r, readRDS myData13,include=FALSE }
if (loadData==0){
# Individual Regression
OriginalData<- SCR_Single_corr_prep_all
ModelData1<-Behav_Single_invAK_corr_prep_all
ModelData2<- Behav_SingleCategory2SortedbyArousal_corr_prep_all
VariableOriginal<-"SCR_Single"
VariableModel1<- "AroRatings_invAK"
VariableModel2<- "Category2_Factor"

RSMIndividualRegression(OriginalData,ModelData1,ModelData2,VariableOriginal,VariableModel1,VariableModel2) 

#Amplitude
SingleSimComparisonCat2<-inner_join(AroRatings_invAK_SCR_Single_tableCorrelation,SCRSingle_Category2SortedbyArousal_tableCorrelation,
                             by = "VP", suffix = c("invAK","Cat2"))

cor.testSingSimComCat2<-cor.test(SingleSimComparisonCat2$CorrelationinvAK,SingleSimComparisonCat2$CorrelationCat2)

 p<- ggplot(SingleSimComparisonCat2, aes(x=CorrelationinvAK, y=CorrelationCat2)) +
  geom_point(shape=21, color = "black",fill="gray75", size=5)+
   theme(legend.position="none")+
   stat_smooth(method = "lm",
              formula = y ~ x,
              geom = "smooth", color = "red")+
   theme_classic()+
 stat_cor(method = "pearson")+
       ggtitle("SCR Single")
   
SCRSingleCorrModCompCat2<- ggMarginal(p ,type="histogram", fill = "slateblue", xparams = list(  bins=100))
}

```

```{r}
SCRSingleCorrModCompCat2

ggarrange(SCR_Single_AroRatings_invAK_Category2_Factor_IndividualPlotRegression[[1]],
SCR_Single_AroRatings_invAK_Category2_Factor_IndividualPlotRegression[[2]],
            labels = c("", "" ),   vjust=-7,
            ncol = 2, nrow =1, widths = c(5,5))
# save.image("RSA_SCR_Pic_VB22_Def.RData")

```


```{r rigdge-plot}
library(ggridges) # ridgeline plot
library(tidyr) # long format
library(colorBlindness)
library(RColorBrewer)
#install.packages("cols4all", dependencies = TRUE)
#library(cols4all)
# long_data <- gather(SingleSimComparisonCat2, key = "model", value = "Correlation", 2:3)
# ggplot(long_data, aes(x=Correlation, y=model))  + geom_density_ridges()
# ### single model alternative based on RSM data
# # STR_VariableModel1_VariableModel2_tableRegression = tableCorrelation
# long_data2 <- gather(STR_VariableModel1_VariableModel2_tableRegression, key = "model", value = "Similarity", 2:3)
# ggplot(long_data2, aes(x=Similarity, y=model))  + geom_density_ridges()+
#   scale_y_discrete(labels = c(VariableModel1, VariableModel2))
### all models
test = cbind(SCRSingle_AroRatings_invAK_Time_NN_tableRegression,SCRSingle_AroRatings_invAK_Category_Factor_tableRegression,SCRSingle_AroRatings_invAK_Category2_Factor_tableRegression, SCRSingle_AroRatings_invAK_Valence_NN_tableRegression)
test2 = test[-c(3,4,6,7,9,10,12,13)]
names(test2)<-c("VP", "Time", "Cat", "Cat2", "Valence")
long_data2 <- gather(test2, key = "model", value = "Similarity", 2:5)
#---------- BAYES t-test: 

#Bayes testing
t.test(test2$Time, mu = 0)

t.test(test2$Cat, mu = 0)
t.test(test2$Cat2, mu = 0)
t.test(test2$Valence, mu = 0)

extractBF(ttestBF( test2$Time), onlybf = TRUE)
  extractBF(ttestBF( test2$Cat), onlybf = TRUE)
  extractBF(ttestBF( test2$Cat2), onlybf = TRUE)
  extractBF(ttestBF( test2$Valence), onlybf = TRUE)

 
ggplot(long_data2, aes(x=Similarity, y=model, fill = model))  + geom_density_ridges()+
    scale_fill_brewer(palette = 4) +
  theme_ridges() + theme(legend.position = "none")+
  labs(x = "rho value", y = "Regressor")+
  geom_vline(xintercept = 0, color = "red", linetype = "dashed")
# colorblind friendly
cols = c("#E69F00"  ,   "#004949"  ,   "#009292" ,    "#FF6DB6"    , "#FFB6DB" ,    "#490092"  ,   "#006DDB" ,
    "#B66DFF"  ,   "#6DB6FF"   ,  "#B6DBFF")
ggplot(long_data2, aes(x=Similarity, y=model, fill = model))  + geom_density_ridges()+
  theme_ridges() + theme(legend.position = "none")+
  labs(x = "rho value", y = "regressor")+
geom_density_ridges(quantile_lines=TRUE,
                      quantile_fun=function(x,...)mean(x)) +
  scale_fill_manual(values = cols)+
  geom_vline(xintercept = 0, color = "red", linetype = "dashed")
#displayAvailablePalette(color="white")

#FINAL GRAPH

cols = c(  "#6DB6FF" , "#004949"  ,    "#FFB6DB","#B66DFF"   )

ggplot(long_data2, aes(x=Similarity, y=model, fill = model, alpha = .2))  + 
  theme_classic() + theme(legend.position = "none")+
  labs(x = "Similarity", y = "")+
  scale_y_discrete(expand = expansion(add = c(0,1)))+
  geom_density_ridges(quantile_lines=TRUE,bandwidth = 0.1,
                      quantile_fun=function(x,...)mean(x), size = 1) +
  scale_fill_manual(values = cols, )+
  geom_vline(xintercept = 0, color = "black", linetype = "dashed", size = 1)+
  scale_x_continuous(breaks= c(-.5,-.25,0, .25,.5,.75), limits= c(-.5,.8))+
  theme(axis.text.x= element_text(size=20),
        axis.text.y= element_blank(), #element_text(size=15),
        axis.title.x =  element_text( size=25,face="bold"),
        axis.title.y = element_text( size=15,face="bold"))



#----------------- Plotting means and STD,
#it needs to be filtered by task
# SCR_RSM$Cat<-ifelse(SCR_RSM$trial_type==2, "Pl",
#                          ifelse(SCR_RSM$trial_type==4, "Un", "Ne"))
# testlm<-lmer(EDA_mean_log~Cat + (1|Vp_ratings), data= SCR_RSM)
# summary(testlm)
SCR_RSMSumm<-SCR_RSM%>%
  group_by(Vp_ratings,trial_type)%>%
  dplyr::summarise(meanSCR= mean(EDA_mean_log,na.rm=T),
                   SDSCR= sd(EDA_mean_log,na.rm=T),
                   meanAro= mean(Aro, na.rm=T),
                   SDAro= sd(Aro, na.rm=T))%>%ungroup

SCR_RSMSumm$Cat<-ifelse(SCR_RSMSumm$trial_type==2, "Pl",
                         ifelse(SCR_RSMSumm$trial_type==4, "Un", "Ne"))

SCR_RSMSumm$Cat<-as.factor(SCR_RSMSumm$Cat)
res.aov2 <- rstatix::anova_test(data = SCR_RSMSumm, dv = meanSCR, 
                                wid = Vp_ratings, within = c(trial_type))
get_anova_table(res.aov2)

res.aov3 <- rstatix::anova_test(data = SCR_RSMSumm, dv = SDSCR, 
                                wid = Vp_ratings, within = c(trial_type))
get_anova_table(res.aov3)

res.aov4 <- rstatix::anova_test(data = SCR_RSMSumm, dv = meanAro, 
                                wid = Vp_ratings, within = c(trial_type))
get_anova_table(res.aov4)

res.aov5 <- rstatix::anova_test(data = SCR_RSMSumm, dv = SDAro, 
                                wid = Vp_ratings, within = c(trial_type))
get_anova_table(res.aov5)
# 
# res.aov4 <- rstatix::anova_test(data = SCR_RSMSumm, dv = meanSCR, covariate= SDSCR,
#                                 wid = Vp_ratings, within = c(trial_type))
# get_anova_table(res.aov4)

testlm<-lmer(meanSCR~Cat*SDSCR + (1|Vp_ratings), data= SCR_RSMSumm)
summary(testlm)

plot_model(testlm, type = "pred", terms = c("SDSCR", "Cat"))



testlm<-lmer(SDSCR~Cat*meanSCR + (1|Vp_ratings), data= SCR_RSMSumm)
summary(testlm)

testlm<-lmer(meanSCR~Cat*meanAro + (1|Vp_ratings), data= SCR_RSMSumm)
summary(testlm)




testlm<-lmer(meanAro~Cat*SDAro + (1|Vp_ratings), data= SCR_RSMSumm)
summary(testlm)


testlm<-lmer(SDAro~Cat*meanAro + (1|Vp_ratings), data= SCR_RSMSumm)
summary(testlm)


testlm<-lmer(trial_type~SDAro*meanAro + (1|Vp_ratings), data= SCR_RSMSumm)
summary(testlm)
plot_model(testlm, type = "pred", terms = c("SDAro", "meanAro"))

testlm<-lmer(trial_type~SDSCR*meanSCR + (1|Vp_ratings), data= SCR_RSMSumm)
summary(testlm)
plot_model(testlm, type = "pred", terms = c("SDSCR", "meanSCR"))


plot_model(testlm, type = "pred", terms = c("SDSCR", "Cat"))

plot_model(testlm, type = "pred", terms = c("SDSCR", "Cat"))
SCR_RSMSumm2<-SCR_RSMSumm%>%
  group_by(trial_type)%>%
  dplyr::summarise(sdmeanSCR= sd(meanSCR, na.rm=T),
                  meanSCR= mean(meanSCR,na.rm=T),
                  sdSDSCR= sd(SDSCR,na.rm=T),
                  SDSCR= mean(SDSCR,na.rm=T),
                   sdmeanAro= sd(meanAro, na.rm=T),
                  sdSDAro= sd(SDAro,na.rm=T),
                  meanAro= mean(meanAro, na.rm=T),
                 SDAro = mean(SDAro, na.rm=T)

)
SCR_RSMSumm2$Cat<-ifelse(SCR_RSMSumm2$trial_type==2, "Pl",
                         ifelse(SCR_RSMSumm2$trial_type==4, "Un", "Ne"))
# plot means and STD
nParticipant<- length(table(SCR_RSMSumm$Vp_ratings))

Plot<-ggplot(data =SCR_RSMSumm2,aes()) +
  #   #Add geom_() objects
  geom_point(aes(x = Cat, y = meanSCR, color= Cat),
             position = position_nudge(x =0), alpha = .8, size = 7) +
  
  geom_errorbar( aes(x = Cat, y = meanSCR,color= Cat,
                     ymin = meanSCR-(sdmeanSCR/sqrt(nParticipant)), ymax = meanSCR+(sdmeanSCR/sqrt(nParticipant))),
                 width = 0.05, size = 2, alpha = 1) +
  
  # geom_line(aes(x =Cat, y = meanSCR, group),
  #           position = position_nudge(x = 0), size = 4) +
  # # scale_y_continuous(breaks=c(0.1,.3,.5,.7,.9),#labels=c("","","", "","","not very good", "","quike ok","","","very good"),
  #                    limits=c(0, .95),expand = expansion(mult = c(0, .1)))+
  theme_classic()+ 
  theme(legend.position="right",
        legend.title= element_text(size= 24, face= "bold"),
        legend.text= element_text(size=20),
        panel.spacing = unit(3, "lines"))+
  theme(axis.text.x= element_text(size=20),
        axis.text.y= element_text(size=24),
        axis.title.x = element_text( size=28,face="bold"),
        axis.title.y = element_text( size=28,face="bold"))+
  xlab("") + ylab("SCR") 



Plot2<-ggplot(data =SCR_RSMSumm2,aes()) +
  #   #Add geom_() objects
  geom_point(aes(x = Cat, y = SDSCR, color= Cat),
             position = position_nudge(x =0), alpha = .8, size = 7) +
  
  geom_errorbar( aes(x = Cat, y = meanSCR,color= Cat,
                     ymin = SDSCR-(sdSDSCR/sqrt(nParticipant)), ymax = SDSCR+(sdSDSCR/sqrt(nParticipant))),
                 width = 0.05, size = 2, alpha = 1) +
  
  # geom_line(aes(x =  Cat, y = SDSCR, group= Cat, color = Cat),
  #           position = position_nudge(x = 0), size = 4) +
  # # scale_y_continuous(breaks=c(0.1,.3,.5,.7,.9),#labels=c("","","", "","","not very good", "","quike ok","","","very good"),
  #                    limits=c(0, .95),expand = expansion(mult = c(0, .1)))+
  theme_classic()+ 
  theme(legend.position="right",
        legend.title= element_text(size= 24, face= "bold"),
        legend.text= element_text(size=20),
        panel.spacing = unit(3, "lines"))+
  theme(axis.text.x= element_text(size=20),
        axis.text.y= element_text(size=24),
        axis.title.x = element_text( size=28,face="bold"),
        axis.title.y = element_text( size=28,face="bold"))+
  xlab("") + ylab("SDSCR") 

Plot3<-ggplot(data =SCR_RSMSumm2,aes()) +
  #   #Add geom_() objects
  geom_point(aes(x = Cat, y = meanAro, color= Cat),
             position = position_nudge(x =0), alpha = .8, size = 7) +
  
  geom_errorbar( aes(x = Cat, y = meanAro,color= Cat,
                     ymin = meanAro-(sdmeanAro/sqrt(nParticipant)), ymax = meanAro+(sdmeanAro/sqrt(nParticipant))),
                 width = 0.05, size = 2, alpha = 1) +
  
  theme_classic()+ 
  theme(legend.position="right",
        legend.title= element_text(size= 24, face= "bold"),
        legend.text= element_text(size=20),
        panel.spacing = unit(3, "lines"))+
  theme(axis.text.x= element_text(size=20),
        axis.text.y= element_text(size=24),
        axis.title.x = element_text( size=28,face="bold"),
        axis.title.y = element_text( size=28,face="bold"))+
  xlab("") + ylab("AroRating") 



Plot4<-ggplot(data =SCR_RSMSumm2,aes()) +
  #   #Add geom_() objects
  geom_point(aes(x = Cat, y = SDAro, color= Cat),
             position = position_nudge(x =0), alpha = .8, size = 7) +
  
  geom_errorbar( aes(x = Cat, y = meanSCR,color= Cat,
                     ymin = SDAro-(sdSDAro/sqrt(nParticipant)), ymax = SDAro+(sdSDAro/sqrt(nParticipant))),
                 width = 0.05, size = 2, alpha = 1) +
  
  # geom_line(aes(x =  Cat, y = SDSCR, group= Cat, color = Cat),
  #           position = position_nudge(x = 0), size = 4) +
  # # scale_y_continuous(breaks=c(0.1,.3,.5,.7,.9),#labels=c("","","", "","","not very good", "","quike ok","","","very good"),
  #                    limits=c(0, .95),expand = expansion(mult = c(0, .1)))+
  theme_classic()+ 
  theme(legend.position="right",
        legend.title= element_text(size= 24, face= "bold"),
        legend.text= element_text(size=20),
        panel.spacing = unit(3, "lines"))+
  theme(axis.text.x= element_text(size=20),
        axis.text.y= element_text(size=24),
        axis.title.x = element_text( size=28,face="bold"),
        axis.title.y = element_text( size=28,face="bold"))+
  xlab("") + ylab("SDAroRating") 



ggarrange(Plot,Plot2 ,Plot3, Plot4, 
       # SCRVector_SCRSingle_IndividualPlot, SCR_Single_SCR_Vector_PermOutput[["Output"]][["PermutationPlot"]],
       labels = c("A", "B", "C", "D" ),
       ncol = 2, nrow =2, widths = c(10,10))



```